Forecasting biodiversity in breeding birds using best practices

### 2017-12-10 manuscript/draft.Rmd
were -> are

where the standard deviation of $\epsilon$ is a free parameter for each site. In
contrast to the "average" model, whose predictions were based on the average
richness across the whole time series, the "naive" model predicts that future
observations will be similar to the *final* observed value (e.g., in our
hindcasts the value observed in `r timeframe$last_train_year`). Moreover,
because the $\epsilon$ values accumulate over time, the confidence intervals
expand rapidly as the predictions extend farther into the future. Despite these
differences, both models' richness predictions are centered on a constant value,
so neither model can anticipate any trends in richness or any responses to
future environmental changes.

>>>>

where the standard deviation of $\epsilon$ is a free parameter for each site. In
contrast to the "average" model, whose predictions are based on the average
richness across the whole time series, the "naive" model predicts that future
observations will be similar to the *final* observed value (e.g., in our
hindcasts the value observed in `r timeframe$last_train_year`). Moreover,
because the $\epsilon$ values accumulate over time, the confidence intervals
expand rapidly as the predictions extend farther into the future. Despite these
differences, both models' richness predictions are centered on a constant value,
so neither model can anticipate any trends in richness or any responses to
future environmental changes.
